SAT Solving for Vesicle Traffic Systems in Cells

### 2017-07-13 paper/pm-1-matrix.tex
fixed-dia

\node[above=4pt of m-1-1] (top-1) {$M_1$};
\node[above=4pt of m-1-2] (top-2) {$M_2$};
\node[above=4pt of m-1-3] (top-3) {$M_3$};
\node[above=4pt of m-1-4] (top-4) {$M_4$};
\node[above=4pt of m-1-5] (top-5) {$M_5$};
\node[above=4pt of m-1-6] (top-6) {$M_6$};
\node[above=4pt of m-1-7] (top-7) {$M_7$};
\node[above=4pt of m-1-8] (top-8) {$M_8$};

\node[left=12pt of m-1-1] (left-1) {$M_1$};
\node[left=12pt of m-2-1] (left-2) {$M_2$};
\node[left=12pt of m-3-1] (left-3) {$M_3$};
\node[left=12pt of m-4-1] (left-4) {$M_4$};
\node[left=12pt of m-5-1] (left-5) {$M_5$};
\node[left=12pt of m-6-1] (left-6) {$M_6$};
\node[left=12pt of m-7-1] (left-7) {$M_7$};
\node[left=12pt of m-8-1] (left-8) {$M_8$};

@@

\caption{Pairing matrix} \label{fig:M1}
\end{figure}

>>>>

\node[above=4pt of m-1-1] (top-1) {$M_0$};
\node[above=4pt of m-1-2] (top-2) {$M_1$};
\node[above=4pt of m-1-3] (top-3) {$M_2$};
\node[above=4pt of m-1-4] (top-4) {$M_3$};
\node[above=4pt of m-1-5] (top-5) {$M_4$};
\node[above=4pt of m-1-6] (top-6) {$M_5$};
\node[above=4pt of m-1-7] (top-7) {$M_6$};
\node[above=4pt of m-1-8] (top-8) {$M_7$};

\node[left=12pt of m-1-1] (left-1) {$M_0$};
\node[left=12pt of m-2-1] (left-2) {$M_1$};
\node[left=12pt of m-3-1] (left-3) {$M_2$};
\node[left=12pt of m-4-1] (left-4) {$M_3$};
\node[left=12pt of m-5-1] (left-5) {$M_4$};
\node[left=12pt of m-6-1] (left-6) {$M_5$};
\node[left=12pt of m-7-1] (left-7) {$M_6$};
\node[left=12pt of m-8-1] (left-8) {$M_7$};

@@

\caption{\textbf{Pairing matrix}. VTS has 3 compartments and 8 molecules. Molecules are numbered 0-7 and and intersection matrix entry describes the fusion dependency. The entry 1 represents pairing, entry $\times$ represents no dependency and rectangles colored $\times$ one represents don't cares. In the right side of the pairing matrix is the graph VTS representation. Everwhere in the graph you can see the flux is maintained, that is every molecule is coming back to it's source node in a cycle. } \label{fig:M1}
\end{figure}
